---
title: "Analyses"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
set.seed(42)
library(fitdistrplus)
library(tidyverse)
library(data.table)
library(ggridges)
library(bayestestR)
library(cutpointr)
library(kableExtra)
library(formattable)
library(cowplot)
library(parallel)
source("src/inputs.R")
source("src/utils.R")
source("src/cutpoint_methods.R")
source("src/summary.R")

do_new_analyses <- FALSE
save_plots <- TRUE
```


Objective: evaluate the NMB associated with cutpoint methods, including the cost-effective cutpoint which is our proposed method that finds the cutpoint that maximises the NMB on the training set.

```{r}

get_nmb <- function() {
  # WTP from Edney et al (2018), Pharmacoeconomics
  WTP <- params$global$WTP

  # treatment_effect taken from: Haines et al. (2010) Archives of Internal Medicine
  treatment_effect <- exp(rnorm(
    1,
    mean = params$falls$treatment_log_hazard$mean,
    sd = params$falls$treatment_log_hazard$sd
  ))

  # taken from abstract of Hill (2015), Lancet
  treatment_cost <- params$falls$treatment_cost

  # taken from Morello et al (2015). MJA

  falls_cost <-
    rgamma(
      1,
      params$falls$falls_cost$shape,
      params$falls$falls_cost$rate
    ) * params$falls$falls_cost$multiplier

  # taken from Latimer et al (2013) Age and Ageing
  fall_eff <- rbeta(
    1,
    params$falls$fall_decrement$shape1,
    params$falls$fall_decrement$shape2
  ) * 0.5 # Latimer conducted 6-month follow-up <- 0.5*utility = QALY

  c(
    "TN" = 0,
    "FN" = -(falls_cost + fall_eff * WTP),
    "TP" = -(falls_cost + WTP * fall_eff) * (1 - treatment_effect) - treatment_cost,
    "FP" = -treatment_cost
  )
}
get_nmb()

# the same as get_nmb for falls but returns only the point estimates.
get_nmb_est <- function() {
  WTP <- params$global$WTP

  # treatment_effect taken from: Haines et al. (2010) Archives of Internal Medicine
  treatment_effect <- exp(params$falls$treatment_log_hazard$mean)

  # taken from abstract of Haines (2010), BMC Medicine
  treatment_cost <- params$falls$treatment_cost

  # taken from Morello et al (2015). MJA

  falls_cost <- 6669 * params$falls$falls_cost$multiplier

  # taken from Latimer et al (2013) Age and Ageing
  fall_eff <- 0.04206168 * 0.5 # Latimer conducted 6-month follow-up <- 0.5*utility = QALY

  c(
    "TN" = 0,
    "FN" = -(falls_cost + fall_eff * WTP),
    "TP" = -(falls_cost + WTP * fall_eff) * (1 - treatment_effect) - treatment_cost,
    "FP" = -treatment_cost
  )
}
get_nmb_est()
```


```{r}
get_nmb_ICU <- function() {
  WTP <- params$global$WTP

  # Treatment effect taken from de Vos et al (2022), Value in Health
  eff_disch <- rbeta(
    1,
    params$icu$ward_eff$shape1,
    params$icu$ward_eff$shape2
  ) * params$icu$ward_eff$multiplier

  # ICU occupancy cost taken from Hicks et al (2019), MJA
  ICU_cost <- rgamma(
    1,
    params$icu$icu_cost$shape,
    params$icu$icu_cost$rate
  ) * params$icu$icu_cost$multiplier

  # Opportunity cost taken from Page et al (2017), BMC HSR
  ICU_opp_cost <- params$icu$opp_cost

  # ICU readmission LOS taken from Chen et al (1998), Crit Care Med
  ICU_readmit <- rgamma(
    1,
    params$icu$icu_readmit_los$shape,
    params$icu$icu_readmit_los$rate,
  )

  c(
    "TN" = eff_disch * WTP,
    "FN" = eff_disch * WTP - ICU_readmit * ICU_cost,
    "TP" = -ICU_cost,
    "FP" = -ICU_cost - ICU_opp_cost
  )
}
get_nmb_ICU()

# Repeat point estimate replacement for ICU
get_nmb_est_ICU <- function() {
  WTP <- params$global$WTP

  # Treatment effect taken from de Vos et al (2022), Value in Health
  eff_disch <- 0.42

  # ICU occupancy cost taken from Hicks et al (2019), MJA
  ICU_cost <- 4375 * params$icu$icu_cost$multiplier

  # Opportunity cost taken from Page et al (2017), BMC HSR
  ICU_opp_cost <- params$icu$opp_cost

  # ICU readmission LOS taken from Chen et al (2021), World Journal of Surgery
  ICU_readmit <- 7.8

  c(
    "TN" = eff_disch * WTP,
    "FN" = eff_disch * WTP - unname(ICU_readmit) * ICU_cost,
    "TP" = -ICU_cost,
    "FP" = -ICU_cost - ICU_opp_cost
  )
}
```


### Run simulation
```{r}

do_simulation <- function(sample_size, n_sims, n_valid, sim_auc, event_rate,
                          fx_costs_training, fx_costs_evaluation,
                          intercept_adjustment = 0, return_calibration_plot = F,
                          seed = 42, ...) {
  if (!is.null(seed)) set.seed(seed)
  if (missing(sample_size)) {
    pmsamp <- pmsampsize::pmsampsize(
      type = "b",
      cstatistic = sim_auc,
      parameters = 1,
      prevalence = event_rate
    )
    sample_size <- pmsamp$sample_size
    min_events <- pmsamp$events
  } else {
    min_events <- round(sample_size * prevalence)
  }
  if (return_calibration_plot) {
    p_calibration <- ggplot() +
      geom_abline()
  }

  i <- 0
  while (i < n_sims) {
    train_sample <- get_sample(auc = sim_auc, n_samples = sample_size, prevalence = event_rate, min_events = min_events)
    valid_sample <- get_sample(auc = sim_auc, n_samples = n_valid, prevalence = event_rate, min_events = 0)
    i <- i + 1
    model <- glm(actual ~ predicted, data = train_sample, family = binomial())

    if (intercept_adjustment != 0) {
      train_log_odds <- predict(model) + intercept_adjustment
      train_sample$predicted <- exp(train_log_odds) / (1 + exp(train_log_odds))

      valid_log_odds <- predict(model, newdata = valid_sample) + intercept_adjustment
      valid_sample$predicted <- exp(valid_log_odds) / (1 + exp(valid_log_odds))
    } else {
      train_sample$predicted <- predict(model, type = "response")
      valid_sample$predicted <- predict(model, type = "response", newdata = valid_sample)
    }

    if (return_calibration_plot) {
      df_calplot <- train_sample %>%
        mutate(bin = ntile(predicted, 10)) %>%
        group_by(bin) %>%
        summarize(
          n = n(),
          bin_pred = mean(predicted),
          bin_prob = mean(actual),
          se = sqrt((bin_prob * (1 - bin_prob)) / n),
          ul = bin_prob + 1.96 * se,
          ll = bin_prob - 1.96 * se
        ) %>%
        ungroup()

      p_calibration <- p_calibration + geom_line(data = df_calplot, aes(x = bin_pred, y = bin_prob), alpha = 0.2)
      p_calibration <- p_calibration + geom_point(data = df_calplot, aes(x = bin_pred, y = bin_prob), alpha = 0.2)
    }


    training_value_vector <- fx_costs_training()

    thresholds <- get_thresholds(
      predicted = train_sample$predicted,
      actual = train_sample$actual,
      costs = training_value_vector
    )

    evaluation_value_vector <- fx_costs_evaluation()

    cost_threshold <- function(pt) {
      classify_samples(
        predicted = valid_sample$predicted,
        actual = valid_sample$actual,
        pt = pt,
        costs = evaluation_value_vector
      )
    }

    results_i <-
      unlist(thresholds) %>%
      map_dbl(cost_threshold) %>%
      t()
    thresholds_i <- unlist(thresholds)
    if (i == 1) {
      df_result <- results_i
      df_thresholds <- thresholds_i
    } else {
      df_result <- rbind(df_result, results_i)
      df_thresholds <- rbind(df_thresholds, thresholds_i)
    }
  } # end simulation loop

  df_result <- as.data.frame.matrix(df_result)
  df_thresholds <- as.data.frame.matrix(df_thresholds)
  rownames(df_thresholds) <- NULL

  df_result <- add_column(df_result, n_sim = 1:nrow(df_result), .before = T)
  df_thresholds <- add_column(df_thresholds, n_sim = 1:nrow(df_thresholds), .before = T)

  res <- list(
    date_time = Sys.time(),
    df_result = df_result,
    df_thresholds = df_thresholds,
    meta_data = list(
      sample_size = sample_size,
      n_sims = n_sims,
      n_valid = n_valid,
      sim_auc = sim_auc,
      event_rate = event_rate,
      fx_costs_training = fx_costs_training,
      fx_costs_evaluation = fx_costs_evaluation
    )
  )

  if (return_calibration_plot) {
    p_calibration <-
      p_calibration +
      theme_bw() +
      labs(
        x = "Predicted Probability",
        y = "Observed Probability"
      )
    res <- append(res, list(calibration_plot = p_calibration))
  }

  res
}


# x <- do_simulation(
#   # sample_size=500,
#   n_sims=100, n_valid=1000, sim_auc=0.6, event_rate=0.01,
#   # fx_costs_training=get_nmb_est_ICU, fx_costs_evaluation=get_nmb_ICU,
#   fx_costs_training=get_nmb_est, fx_costs_evaluation=get_nmb,
#   plot_type = "histogram",
#   scale=1
# )
```

# (mis)calibration experiment

## do simulations
```{r}
cfg_falls <- list(
  n_sim = 500,
  n_valid = 10000,
  sim_auc = 0.7,
  event_rate = 0.036
)
if (do_new_analyses | !file.exists("output/calibration_experiment/calibration_simulations-falls.rds")) {
  f_do_sim_calibration_falls <- function(intercept_adjustment, seed) {
    do_simulation(
      n_sims = cfg_falls$n_sim, n_valid = cfg_falls$n_valid,
      sim_auc = cfg_falls$sim_auc, event_rate = cfg_falls$event_rate,
      fx_costs_training = get_nmb_est, fx_costs_evaluation = get_nmb,
      intercept_adjustment = intercept_adjustment, return_calibration_plot = T,
      seed = seed
    )
  }

  x_calibrated <- f_do_sim_calibration_falls(0, 1)
  x_adjusted_up <- f_do_sim_calibration_falls(1, 2)
  x_adjusted_down <- f_do_sim_calibration_falls(-1, 3)
  x_adjusted_up2 <- f_do_sim_calibration_falls(2, 4)
  x_adjusted_down2 <- f_do_sim_calibration_falls(-2, 5)

  calibration_experiment_list <- list(
    up2 = x_adjusted_up2,
    up1 = x_adjusted_up,
    calibrated = x_calibrated,
    down1 = x_adjusted_down,
    down2 = x_adjusted_down2
  )

  saveRDS(calibration_experiment_list, "output/calibration_experiment/calibration_simulations-falls.rds")
}

cfg_icu <- list(
  n_sim = 500,
  n_valid = 10000,
  sim_auc = 0.7,
  event_rate = 0.025
)

if (do_new_analyses | !file.exists("output/calibration_experiment/calibration_simulations-icu.rds")) {
  f_do_sim_calibration_icu <- function(intercept_adjustment, seed) {
    do_simulation(
      n_sims = cfg_icu$n_sim, n_valid = cfg_icu$n_valid,
      sim_auc = cfg_icu$sim_auc, event_rate = cfg_icu$event_rate,
      fx_costs_training = get_nmb_est_ICU, fx_costs_evaluation = get_nmb_ICU,
      intercept_adjustment = intercept_adjustment, return_calibration_plot = T,
      seed = seed
    )
  }

  x_calibrated <- f_do_sim_calibration_icu(0, 1)
  x_adjusted_up <- f_do_sim_calibration_icu(1, 2)
  x_adjusted_down <- f_do_sim_calibration_icu(-1, 3)
  x_adjusted_up2 <- f_do_sim_calibration_icu(2, 4)
  x_adjusted_down2 <- f_do_sim_calibration_icu(-2, 5)

  calibration_experiment_list <- list(
    up2 = x_adjusted_up2,
    up1 = x_adjusted_up,
    calibrated = x_calibrated,
    down1 = x_adjusted_down,
    down2 = x_adjusted_down2
  )

  saveRDS(calibration_experiment_list, "output/calibration_experiment/calibration_simulations-icu.rds")
}
```

## make plots
```{r}

cols_rename <- c(
  "Treat All" = "treat_all",
  "Treat None" = "treat_none",
  "Value- Optimising" = "cost_effective",
  "Closest to (0, 1)" = "er",
  "Youden" = "youden",
  "Sens-Spec product" = "cz",
  "Index of Union" = "iu",
  "Cost- Minimising" = "cost_minimising"
)


exclude_groups <- TRUE
# save_plots <- TRUE
if (exclude_groups) {
  groups_remove <- c("Treat None", "Closest to (0, 1)", "Youden", "Sens-Spec product", "Index of Union")
  rel_widths_inb_and_calibration_plots <- c(0.4, 0.25)
  final_plot_width <- 6
  plot_suffix <- "main-doc-figure"
} else {
  groups_remove <- c()
  rel_widths_inb_and_calibration_plots <- c(0.6, 0.25)
  final_plot_width <- 7.3
  plot_suffix <- "supplementary-figure"
}


calibration_experiment_falls <- readRDS("output/calibration_experiment/calibration_simulations-falls.rds")

falls_x_lims <- rep(list(list(min = -220, max = 75)), length(calibration_experiment_falls))

inb_plots_falls <- get_plot_list(
  out_list = calibration_experiment_falls,
  rename_vector = cols_rename,
  inb_ref_col = "Treat All",
  groups_remove = groups_remove,
  get_what = "inb",
  agg_line_size = 1,
  x_lims_list = falls_x_lims
  # extra_theme=theme(panel.spacing  = unit(0, "lines")) # comment this line out to keep default spacing between facets
)

calibration_plots_falls <- get_plot_list(
  out_list = calibration_experiment_falls,
  get_what = "calibration"
)

inb_plots_falls <- keep_only_first_plot_strip(inb_plots_falls)

inb_cowplot_falls <- plot_grid(plotlist = inb_plots_falls, ncol = 1, rel_heights = c(0.375, rep(0.3, length(inb_plots_falls) - 1)))


# cowplot::plot_grid(plotlist=calibration_plots, ncol=1)
empty_space <- ggplot() +
  theme_bw() +
  theme(
    axis.line = element_line(colour = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()
  )
calibration_cowplot_falls <- plot_grid(
  plotlist = c(list(empty_space), calibration_plots_falls),
  ncol = 1,
  rel_heights = c(0.075, rep(0.3, length(calibration_plots_falls)))
)

# calibration_cowplot <- plot_grid(plotlist=calibration_plots, ncol=1)
combined_fig_falls <- plot_grid(inb_cowplot_falls, calibration_cowplot_falls, ncol = 2, rel_widths = rel_widths_inb_and_calibration_plots)

if (save_plots) {
  ggsave(filename = glue::glue("output/calibration_experiment/calibration_plots-falls_{plot_suffix}.jpeg"), plot = combined_fig_falls, dpi = 600, height = 8, width = final_plot_width)
}


calibration_experiment_icu <- readRDS("output/calibration_experiment/calibration_simulations-icu.rds")

falls_x_lims <- rep(list(list(min = -5000, max = 10000)), length(calibration_experiment_icu))

inb_plots_icu <- get_plot_list(
  out_list = calibration_experiment_icu,
  rename_vector = cols_rename,
  inb_ref_col = "Treat All",
  groups_remove = groups_remove,
  get_what = "inb",
  agg_line_size = 1
)

calibration_plots_icu <- get_plot_list(
  out_list = calibration_experiment_icu,
  get_what = "calibration"
)

inb_plots_icu <- keep_only_first_plot_strip(inb_plots_icu)

inb_cowplot_icu <- plot_grid(plotlist = inb_plots_icu, ncol = 1, rel_heights = c(0.375, rep(0.3, length(inb_plots_icu) - 1)))

calibration_cowplot_icu <- plot_grid(
  plotlist = c(list(empty_space), calibration_plots_icu),
  ncol = 1,
  rel_heights = c(0.075, rep(0.3, length(calibration_plots_icu)))
)

combined_fig_icu <- plot_grid(inb_cowplot_icu, calibration_cowplot_icu, ncol = 2, rel_widths = rel_widths_inb_and_calibration_plots)
combined_fig_icu
if (save_plots) {
  ggsave(filename = glue::glue("output/calibration_experiment/calibration_plots-icu_{plot_suffix}.jpeg"), plot = combined_fig_icu, dpi = 600, height = 8, width = final_plot_width)
}
```

## combine the two case studies for main-doc figure
```{r}
combined_icu_and_falls_plot <- plot_grid(
  combined_fig_icu, combined_fig_falls,
  rel_widths = c(0.5, 0.5),
  labels = c("A", "B")
)

if (save_plots) {
  ggsave(
    filename = "output/calibration_experiment/calibration_plots-main-figure-combined.jpeg",
    plot = combined_icu_and_falls_plot, dpi = 600, height = 8, width = 10
  )
}
```

# Primary analyses

```{r, fig.height=10, fid.width=7}
if (do_new_analyses | !file.exists("output/primary_analyses/falls_primary_analyses.rds")) {
  falls_simulation <-
    do_simulation(
      n_sims = 5000, n_valid = 10000, sim_auc = 0.7, event_rate = 0.036,
      fx_costs_training = get_nmb_est, fx_costs_evaluation = get_nmb
    )
  saveRDS(falls_simulation, "output/primary_analyses/falls_primary_analyses.rds")
}
falls_simulation <- readRDS("output/primary_analyses/falls_primary_analyses.rds")

if (do_new_analyses | !file.exists("output/primary_analyses/falls_primary_analyses.rds")) {
  icu_simulation <-
    do_simulation(
      n_sims = 5000, n_valid = 10000, sim_auc = 0.7, event_rate = 0.01,
      fx_costs_training = get_nmb_est_ICU, fx_costs_evaluation = get_nmb_ICU
    )
  saveRDS(icu_simulation, "output/primary_analyses/icu_primary_analyses.rds")
}
icu_simulation <- readRDS("output/primary_analyses/icu_primary_analyses.rds")
```

## Plots with most realistic AUC and event rate for each use-case

```{r}
cols_rename <- c(
  "Treat All" = "treat_all",
  "Treat None" = "treat_none",
  "Value- Optimising" = "cost_effective",
  "Closest to (0, 1)" = "er",
  "Youden" = "youden",
  "Sens-Spec product" = "cz",
  "Index of Union" = "iu",
  "Cost- Minimising" = "cost_minimising"
)

PA_CFG <- list(agg_line_size = 1)

p_falls_nmb <-
  falls_simulation$df_result %>%
  # select(-cost_minimising) %>%
  rename(any_of(cols_rename)) %>%
  plot_fw_histogram(
    hdi = F,
    plot_labels = labs(x = "Incremental Net Monetary Benefit (AUD)\n", y = ""),
    inb_ref_col = "Treat All",
    agg_line_size = PA_CFG$agg_line_size
  )



p_falls_cutpoints <-
  falls_simulation$df_thresholds %>%
  select(-treat_all, -treat_none) %>%
  # select(-cost_minimising) %>%
  rename(., any_of(cols_rename)) %>%
  plot_fw_histogram(
    hdi = F,
    plot_labels = labs(x = "Selected cutpoint\n", y = ""),
    dollar_format = F,
    agg_line_size = PA_CFG$agg_line_size
  )



p_icu_nmb <-
  icu_simulation$df_result %>%
  rename(any_of(cols_rename)) %>%
  plot_fw_histogram(
    hdi = F,
    plot_labels = labs(x = "Incremental Net Monetary Benefit (AUD)\n", y = ""),
    inb_ref_col = "Treat None",
    agg_line_size = PA_CFG$agg_line_size
  )

p_icu_cutpoints <-
  icu_simulation$df_thresholds %>%
  select(-treat_all, -treat_none) %>%
  rename(., any_of(cols_rename)) %>%
  plot_fw_histogram(
    hdi = F,
    plot_labels = labs(x = "Selected cutpoint\n", y = ""),
    dollar_format = F,
    agg_line_size = PA_CFG$agg_line_size
  )


plot_grid(
  plotlist = list(
    p_icu_nmb, p_falls_nmb,
    p_icu_cutpoints, p_falls_cutpoints
  ),
  labels = LETTERS[1:4],
  ncol = 2
)

if (save_plots) {
  ggsave(filename = "output/primary_analyses/primary_results.jpeg", dpi = 600, height = 7, width = 11)
}
```


## Table with most realistic AUC and event rate for each use-case
```{r}
falls_summary <- do.call(
  get_summary,
  c(
    falls_simulation$meta_data,
    list(
      data = falls_simulation$df_result, agg_fx = median, hdi = F, ci = 0.95,
      recode_methods_vector = cols_rename, inb_ref_col = "treat_all"
    )
  )
)

icu_summary <- do.call(
  get_summary,
  c(
    icu_simulation$meta_data,
    list(
      data = icu_simulation$df_result, agg_fx = median, hdi = F, ci = 0.95,
      recode_methods_vector = cols_rename, inb_ref_col = "treat_none"
    )
  )
)

# primary_analyses_table
primary_analyses_table <-
  rbind(icu_summary, falls_summary) %>%
  select(method, summary, n_best_percent) %>%
  {
    \(d){
      names(d) <- c(
        "Cutpoint method",
        glue::glue("Incremental Net Monetary Benefit (median [{percent(0.95, digits=0)} Intervals])"),
        "Best performing [n (%)]"
      )
      return(d)
    }
  }() %>%
  formattable() %>%
  kable(escape = F) %>%
  pack_rows(
    index = c(
      "ICU readmission (reference group: Treat None)" = nrow(icu_summary),
      "Inpatient falls (reference group: Treat All)" = nrow(falls_summary)
    )
  ) %>%
  kable_styling()

save_kable(primary_analyses_table, file = "output/primary_analyses/primary_analyses.html")
```


  
```{r, eval=F}

# primary analyses for deliverable (falls only and remove cost-minimising cutpoint method)
do.call(
  get_summary,
  c(
    falls_simulation$meta_data,
    list(
      # data = select(falls_simulation$df_result, -cost_minimising),
      data = falls_simulation$df_result,
      agg_fx = median, hdi = F, ci = 0.95,
      recode_methods_vector = cols_rename, inb_ref_col = "treat_all"
    )
  )
) %>%
  select(
    "Cutpoint method" = method,
    "Incremental Net Monetary Benefit (AUD)" = summary,
    "Best performing [n (%)]" = n_best_percent
  ) %>%
  formattable() %>%
  kable(
    escape = F,
    caption = glue::glue("Incremental Net Monetary Benefit presented as median [{percent(0.95, digits=0)} Intervals]")
  ) %>%
  kable_styling() %>%
  save_kable(file = "output/primary_analyses/primary_results_falls-only_for-deliverables.html")
```


```{r, fig.height=24, fig.width=12}
simulation_config <- list(
  n_sims = 5000,
  n_valid = 10000
)

g_falls <- expand.grid(
  sim_auc = c(0.55, 0.7, 0.85),
  event_rate = c(0.01, 0.036, 0.1)
  # sim_auc=c(0.7),
  # event_rate=seq(0.01, 0.075, 0.005)
)

g_icu <- expand.grid(
  sim_auc = c(0.55, 0.7, 0.85),
  event_rate = c(0.01, 0.025, 0.1)
)

if (do_new_analyses | !file.exists("output/sensitivity_analyses/falls_sensitivity_analyses.rds")) {
  n_cluster <- detectCores() - 2
  cl <- makeCluster(n_cluster)
  cl <- parallelly::autoStopCluster(cl)

  clusterExport(cl, {
    c("do_simulation", "g_falls", "g_icu", "get_nmb", "get_nmb_est", "get_nmb_ICU", "get_nmb_est_ICU", "params", "simulation_config")
  })

  invisible(clusterEvalQ(cl, {
    library(tidyverse)
    library(data.table)
    library(ggridges)
    library(bayestestR)
    library(cutpointr)
    source("src/utils.R")
    source("src/cutpoint_methods.R")
    source("src/summary.R")
  }))


  ll_falls <- parLapply(
    cl,
    1:nrow(g_falls),
    function(i) {
      do.call(
        do_simulation,
        c(
          simulation_config,
          list(
            sim_auc = g_falls$sim_auc[i],
            event_rate = g_falls$event_rate[i],
            fx_costs_training = get_nmb_est,
            fx_costs_evaluation = get_nmb
          )
        )
      )
    }
  )

  saveRDS(ll_falls, "output/sensitivity_analyses/falls_sensitivity_analyses.rds")
}

if (do_new_analyses | !file.exists("output/sensitivity_analyses/falls_sensitivity_analyses.rds")) {
  n_cluster <- detectCores() - 2
  cl <- makeCluster(n_cluster)
  cl <- parallelly::autoStopCluster(cl)

  clusterExport(cl, {
    c("do_simulation", "g_falls", "g_icu", "get_nmb", "get_nmb_est", "get_nmb_ICU", "get_nmb_est_ICU", "params", "simulation_config")
  })

  invisible(clusterEvalQ(cl, {
    library(tidyverse)
    library(data.table)
    library(ggridges)
    library(bayestestR)
    library(cutpointr)
    source("src/utils.R")
    source("src/cutpoint_methods.R")
    source("src/summary.R")
  }))

  ll_icu <- parLapply(
    cl,
    1:nrow(g_icu),
    function(i) {
      do.call(
        do_simulation,
        c(
          simulation_config,
          list(
            sim_auc = g_icu$sim_auc[i],
            event_rate = g_icu$event_rate[i],
            fx_costs_training = get_nmb_est_ICU,
            fx_costs_evaluation = get_nmb_ICU
          )
        )
      )
    }
  )

  saveRDS(ll_icu, "output/sensitivity_analyses/icu_sensitivity_analyses.rds")
}


# save specific screen for falls across event rates
# saveRDS(ll_falls, "output/sensitivity_analyses/falls_sensitivity_analyses2.rds")

# load simulation results
ll_falls <- readRDS("output/sensitivity_analyses/falls_sensitivity_analyses.rds")
ll_icu <- readRDS("output/sensitivity_analyses/icu_sensitivity_analyses.rds")
```

```{r}

# falls_inb_plots <- get_plot_list(
#   ll_falls, cols_rename,
#   get_what = "inb",
#   inb_ref_col = "Treat All", groups_remove = "Cost- Minimising"
# )
#
# falls_cp_plots <- get_plot_list(ll_falls, cols_rename, get_what = "cutpoints")
#
# plot_grid(
#   plotlist = c(falls_inb_plots, falls_cp_plots),
#   nrow = 2,
#   labels = rep(g_falls$event_rate, 2)
# )
#
# if (save_plots) {
#   ggsave(filename = "output/sensitivity_analyses/falls_simulations_inb_for-deliverables_sanity-check.jpeg", height = 10, width = 45)
# }
```



# save plots from sensitivity analyses
```{r}
# FALLS
falls_axis_limits <- c(
  rep(list(list(min = -50, max = 100)), 3),
  rep(list(list(min = -300, max = 100)), 3),
  rep(list(list(min = -800, max = 100)), 3)
)

falls_inb_plots <- get_plot_list(
  ll_falls, cols_rename,
  get_what = "inb", inb_ref_col = "Treat All",
  # groups_remove = "Cost- Minimising",
  only_show_interval = F,
  x_lims_list = falls_axis_limits
)

# add labels to left most graphs for event rate
event_rate_str <- function(rate) glue::glue("Event Rate = {rate}")
model_auc_str <- function(auc) glue::glue("Model AUC = {auc}")

falls_inb_plots[[1]] <- falls_inb_plots[[1]] + xlab(event_rate_str(g_falls$event_rate[1]))
falls_inb_plots[[4]] <- falls_inb_plots[[4]] + xlab(event_rate_str(g_falls$event_rate[4]))
falls_inb_plots[[7]] <- falls_inb_plots[[7]] + xlab(event_rate_str(g_falls$event_rate[7]))

falls_inb_plots[[7]] <- falls_inb_plots[[7]] + ylab(model_auc_str(g_falls$sim_auc[7]))
falls_inb_plots[[8]] <- falls_inb_plots[[8]] + ylab(model_auc_str(g_falls$sim_auc[8]))
falls_inb_plots[[9]] <- falls_inb_plots[[9]] + ylab(model_auc_str(g_falls$sim_auc[9]))


for (i in 1:length(falls_inb_plots)) {
  falls_inb_plots[[i]] <- falls_inb_plots[[i]] +
    theme(
      plot.margin = unit(c(0, 0, 0, 0), "cm")
    )
}

# add border to primary analyses within panels
falls_inb_plots[[5]] <-
  falls_inb_plots[[5]] +
  theme(
    strip.background = element_rect(fill = "#ff8ba0")
  )

plot_grid(
  plotlist = falls_inb_plots,
  ncol = length(unique(g_falls$sim_auc))
)

if (save_plots) {
  ggsave(filename = "output/sensitivity_analyses/falls_simulations_inb.jpeg", height = 24 * 0.5, width = 15)
}

icu_axis_limits <- c(
  rep(list(list(min = -10000, max = 1000)), 3),
  rep(list(list(min = -10000, max = 4000)), 3),
  rep(list(list(min = -10000, max = 20000)), 3)
)

# ICU discharge
icu_inb_plots <- get_plot_list(
  ll_icu, cols_rename,
  get_what = "inb", inb_ref_col = "Treat None",
  # groups_remove = "Cost- Minimising",
  only_show_interval = F,
  x_lims_list = icu_axis_limits
)

icu_inb_plots[[1]] <- icu_inb_plots[[1]] + xlab(event_rate_str(g_icu$event_rate[1]))
icu_inb_plots[[4]] <- icu_inb_plots[[4]] + xlab(event_rate_str(g_icu$event_rate[4]))
icu_inb_plots[[7]] <- icu_inb_plots[[7]] + xlab(event_rate_str(g_icu$event_rate[7]))

icu_inb_plots[[7]] <- icu_inb_plots[[7]] + ylab(model_auc_str(g_icu$sim_auc[7]))
icu_inb_plots[[8]] <- icu_inb_plots[[8]] + ylab(model_auc_str(g_icu$sim_auc[8]))
icu_inb_plots[[9]] <- icu_inb_plots[[9]] + ylab(model_auc_str(g_icu$sim_auc[9]))

for (i in 1:length(icu_inb_plots)) {
  icu_inb_plots[[i]] <- icu_inb_plots[[i]] +
    theme(
      plot.margin = unit(c(0, 0, 0, 0), "cm"),
    )
}

# add border to primary analyses within panels
icu_inb_plots[[5]] <-
  icu_inb_plots[[5]] +
  theme(
    strip.background = element_rect(fill = "#ff8ba0")
  )


plot_grid(
  plotlist = icu_inb_plots,
  ncol = length(unique(g_icu$sim_auc))
)

if (save_plots) {
  ggsave(filename = "output/sensitivity_analyses/icu_simulations_inb.jpeg", height = 24 * 0.5, width = 15)
}
```

```{r}
# save selected cutpoints plots
# cowplot::plot_grid(
#   plotlist=get_plot_list(ll_falls, cols_rename, get_what="cutpoints"),
#   ncol=length(unique(g_falls$sim_auc))
# )
# ggsave(filename="output/falls_simulations_thresholds.jpeg", height=24, width=12)
#
# cowplot::plot_grid(
#   plotlist=get_plot_list(ll_icu, cols_rename, get_what="cutpoints"),
#   ncol=length(unique(g_icu$sim_auc))
# )
# ggsave(filename="output/icu_simulations_thresholds.jpeg", height=24, width=12)
```


```{r}
make_table(
  ll_falls,
  get_what = "inb", rename_vector = cols_rename,
  save_path = "output/sensitivity_analyses/falls_inb_summary.html",
  inb_ref_col = "Treat All"
)

make_table(
  ll_falls,
  get_what = "cutpoints", rename_vector = cols_rename,
  save_path = "output/sensitivity_analyses/falls_thresholds_summary.html"
)

make_table(
  ll_icu,
  get_what = "inb", rename_vector = cols_rename,
  save_path = "output/sensitivity_analyses/icu_inb_summary.html",
  inb_ref_col = "Treat None"
)

make_table(
  ll_icu,
  get_what = "cutpoints", rename_vector = cols_rename,
  save_path = "output/sensitivity_analyses/icu_thresholds_summary.html"
)
```

# bonus figure with similar graphic to shiny app
```{r}
example_cfg <- list(
  auc = 0.85,
  event_rate = 0.15,
  sample_size = 1000,
  min_events = 0.1 * 1000
)

train_data <- get_sample(
  auc = example_cfg$auc,
  n_samples = example_cfg$sample_size,
  prevalence = example_cfg$event_rate,
  min_events = example_cfg$min_events
)

model <- glm(actual ~ predicted, data = train_data, family = binomial())

train_data$preds_proba <- predict(model, type = "response")

thresholds_df <- predictNMB::get_thresholds(
  predicted = train_data$preds_proba,
  actual = train_data$actual,
  nmb = get_nmb_est()
) %>%
  as.data.frame() %>%
  rename("value" = 1) %>%
  rownames_to_column("method") %>%
  filter(method %in% c("all", "none", "value_optimising", "youden")) %>%
  mutate(
    method = recode(
      method,
      "all" = "Treat all",
      "none" = "Treat none",
      "value_optimising" = "Value-optimising",
      "youden" = "Youden Index"
    )
  )

plot_data <-
  train_data %>%
  mutate(
    actual = ifelse(actual == 0, "Non-faller", "Faller"),
    actual = factor(actual, levels = c("Non-faller", "Faller"))
  )

example_plot_1 <-
  ggplot() +
  geom_histogram(
    data = plot_data,
    aes(x = preds_proba, fill = actual),
    alpha = 0.6,
    position = "identity",
    bins = 50
  ) +
  geom_segment(
    data = thresholds_df,
    aes(x = value, xend = value, y = 0, yend = Inf, col = method),
    size = 1.5
  ) +
  geom_text(
    data = thresholds_df,
    aes(x = value + 0.025, y = 150, label = method, col = method),
    hjust = 1,
    angle = 90,
    size = 3.3,
    show.legend = FALSE
  ) +
  scale_color_brewer(type = "qual", palette = "Dark2") +
  theme_bw() +
  labs(
    y = "Frequency (count)",
    x = "Predicted probability of fall (%)",
    col = "Cutpoint method",
    fill = ""
  ) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(legend.position = "left")
```

```{r}

fx_get_sens_spec <- function(actual, predicted, cutpoint) {
  cm <-
    data.frame(actual = actual, proba = predicted) %>%
    group_by(actual, predicted = proba > cutpoint) %>%
    summarize(n = n(), .groups = "drop") %>%
    ungroup()

  # if the cutpoint is above or below ALL predicted probs, add the empty rows to confusion matrix
  if (nrow(cm) != 4) {
    cm <- rbind(
      cm,
      data.frame(
        actual = c(0, 1),
        predicted = !unique(cm$predicted),
        n = 0
      )
    )
  }
  cp_fp <-
    cm %>%
    filter(predicted == 1, actual == 0) %>%
    pull(n)

  cp_fn <-
    cm %>%
    filter(predicted == 0, actual == 1) %>%
    pull(n)

  cp_tp <-
    cm %>%
    filter(predicted == 1, actual == 1) %>%
    pull(n)

  cp_tn <-
    cm %>%
    filter(predicted == 0, actual == 0) %>%
    pull(n)


  c(
    "sensitivity" = sensitivity(tp = cp_tp, fn = cp_fn),
    "specificity" = specificity(fp = cp_fp, tn = cp_tn)
  )
}

f_get_sens <- function(cutpoint) {
  fx_get_sens_spec(
    actual = train_data$actual,
    predicted = train_data$preds_proba,
    cutpoint = cutpoint
  )["sensitivity"]
}

f_get_spec <- function(cutpoint) {
  fx_get_sens_spec(
    actual = train_data$actual,
    predicted = train_data$preds_proba,
    cutpoint = cutpoint
  )["specificity"]
}

thresholds_df <-
  thresholds_df %>%
  rowwise() %>%
  mutate(
    specificity = f_get_spec(value),
    sensitivity = f_get_sens(value)
  )

f_make_proc_df <- function() {
  probs <- train_data$preds_proba
  l <- lapply(
    probs,
    function(x) {
      fx_get_sens_spec(
        actual = train_data$actual,
        predicted = train_data$preds_proba,
        cutpoint = x
      )
    }
  )

  cbind(preds_proba = probs, do.call("rbind", l))
}

proc_df <- f_make_proc_df()

proc_df2 <-
  proc_df %>%
  as.data.frame() %>%
  select(preds_proba, sensitivity, specificity = specificity1)


example_plot_2 <-
  ggplot() +
  geom_point(
    data = proc_df2,
    aes(sensitivity, specificity),
    size = 1,
    shape = 15
  ) +
  geom_point(
    data = thresholds_df,
    aes(x = sensitivity, y = specificity, col = method),
    size = 4,
    show.legend = FALSE
  ) +
  scale_x_reverse() +
  theme_bw() +
  labs(
    y = "Specificity",
    x = "Sensitivity",
    col = "Cutpoint method"
  ) +
  scale_color_brewer(palette = "Dark2") +
  coord_equal()
```


# combine the two plots for example figure
```{r}
shared_legend <- cowplot::get_legend(example_plot_1)

p_combined <- plot_grid(
  shared_legend,
  example_plot_1 + theme(legend.position = "none", aspect.ratio = 1),
  example_plot_2,
  nrow = 1,
  rel_widths = c(0.15, 0.5, 0.5)
)

if (save_plots) {
  ggsave(
    filename = "output/example-cutpoint-figure.jpeg", dpi = 600,
    plot = p_combined, height = 4 * 1.3, width = 8 * 1.3
  )
}
```

