---
title: "Experiment 1"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
set.seed(42)
library(tidyverse)
library(data.table)
library(cutpointr)
source("src/inputs.R")
source("src/utils.R")
source("src/cutpoint_methods.R")
```


Question: What are the differences in NMB between models where the Probability threshold was based on the currently available methods versus costs-based selection. (Hospital falls as a use case.)

1. Define costs of a TP, TN, FP, FN of falls classification (option to move this into the loop where costs are sampled from a distributions to account for uncertainty in their estimates in the literature)
    * FP have cost of applying intervention
    * FN have cost of patient fall
    * TP have cost of intervention + cost of fall*(1-effectiveness of intervention on rate of falls)
    * TN are cost $0
2. Select appropriate ranges for model AUC (~0.75?) and prevalence (~3%) for comparable clinical prediction model for falls.
3. For sample sizes (N) in [100, 500, 1000]: (repeat 500 times at each sample size)
    * Get training data by sampling observed predictor values and outcome by transforming AUC into Cohens' D and sampling from two normal distributions, the first (negative events) with mean=0 and the second (positive events) with mean=Cohens'D. (Both with sd=1.)
    * Fit a logistic regression model using this sampled data.
    * Fit predicted probabilities to the training data and use these to obtain probability thresholds using each method.
    * Get validation data using the same approach but with n=1000.
    * Use the previously fit model to estimate probabilities for validation data.
    * Evaluate the thresholds selected using the training data on the validation data, in terms of mean cost per patient.
4. Measure differences in NMB on validation sample dependent on use of currently available methods and cost-based approach to determine threshold.
5. Observe whether this relationship is dependent on the sample size taken
6. ???


```{r}

get_nmb <- function(){
  # WTP from Edney et al (2018), Pharmacoeconomics
  WTP <- params$global$WTP
  
  # treatment_effect taken from: Haines et al. (2010) Archives of Internal Medicine
  treatment_effect <- exp(rnorm(
    1, 
    mean=params$falls$treatment_log_hazard$mean,
    sd=params$falls$treatment_log_hazard$sd
  ))
  
  # taken from abstract of Haines (2010), BMC Medicine
  treatment_cost <- params$falls$treatment_cost
  
  # taken from Morello et al (2015). MJA
  
  falls_cost <- 
    rgamma(
      1, 
      params$falls$falls_cost$shape, 
      params$falls$falls_cost$rate
    ) * params$falls$falls_cost$multiplier
  
  #taken from Latimer et al (2013) Age and Ageing
  fall_eff <- rbeta(
    1,
    params$falls$fall_decrement$shape1,
    params$falls$fall_decrement$shape2
  ) * 0.5 #Latimer conducted 6-month follow-up <- 0.5*utility = QALY
    
  c(
    "TN"=0,
    "FN"=-falls_cost - fall_eff*WTP,
    "TP"=-falls_cost*(1-treatment_effect) - treatment_cost - fall_eff*WTP,
    "FP"=-treatment_cost
  )
}
get_nmb()


```


```{r}
get_nmb_ICU <- function(){
  
  WTP <- params$global$WTP

  # Treatment effect taken from de Vos et al (2022), Value in Health
  eff_disch <- rbeta(
    1,
    params$icu$ward_eff$shape1,
    params$icu$ward_eff$shape2
  ) * params$icu$ward_eff$multiplier
  
  # ICU occupancy cost taken from Hicks et al (2019), MJA
  ICU_cost <- rgamma(
    1, 
    params$icu$icu_cost$shape,
    params$icu$icu_cost$scale
  ) * params$icu$icu_cost$multiplier
  
  # Opportunity cost taken from Page et al (2017), BMC HSR
  ICU_opp_cost <- params$icu$opp_cost
  
  # ICU readmission cost taken from Tong et al (2021), World Journal of Surgery
  ICU_readmit <- rnorm(
    1, 
    params$icu$icu_readmit_cost$mean,
    params$icu$icu_readmit_cost$sd
  ) * params$icu$icu_readmit_cost$multiplier
  
  c(
    "TN"=eff_disch*WTP,
    "FN"=eff_disch*WTP - ICU_readmit,
    "TP"=-ICU_cost,
    "FP"=-ICU_cost + ICU_opp_cost
  )
}
get_nmb_ICU()

```


### Run simulation
```{r}

do_simulation <- function(sample_size, n_sims, n_valid, sim_auc, event_rate, 
                          fx_costs, resample_values=TRUE, 
                          get_what=c("data", "plot"), plot_type="boxplot",
                          seed=42){
  if(!is.null(seed)) set.seed(seed)
  
  i <- 0
  while(i < n_sims){
    train_sample <- get_sample(auc=sim_auc, n_samples=sample_size, prevalence=event_rate)
    valid_sample <- get_sample(auc=sim_auc, n_samples=n_valid, prevalence=event_rate)
    if(length(unique(train_sample$actual))!=2 | length(unique(valid_sample$actual))!=2){
      next
    }
    i <- i + 1
    model <- glm(actual~predicted, data=train_sample, family=binomial())
    train_sample$predicted <- predict(model, type="response")

    
    valid_sample$predicted <- predict(model, type="response", newdata=valid_sample)
    
    value_vector <- fx_costs()
    
    thresholds <- get_thresholds(
      predicted=train_sample$predicted, 
      actual=train_sample$actual,
      costs=value_vector
    )
    
    if(resample_values){
      value_vector <- fx_costs()
    }
    
    cost_threshold <- function(pt){
      classify_samples(
        predicted=valid_sample$predicted,
        actual=valid_sample$actual,
        pt=pt,
        costs=value_vector
      )
    }
    
    results_i <-
      unlist(thresholds) %>%
      map_dbl(cost_threshold) %>%
      t()
    thresholds_i <- unlist(thresholds)
    if(i==1){
      df_result <- results_i
      df_thresholds <- thresholds_i
    } else {
      df_result <- rbind(df_result, results_i)
      df_thresholds <- rbind(df_thresholds, thresholds_i)
    }
  }
  
  df_result <- as.data.frame.matrix(df_result)
  df_thresholds <- as.data.frame.matrix(df_thresholds)
  rownames(df_thresholds) <- NULL
  
  df_result <- add_column(df_result, n_sim=1:nrow(df_result), .before=T)
  df_thresholds <- add_column(df_thresholds, n_sim=1:nrow(df_thresholds), .before=T)
  
  pts <- round(colMeans(df_thresholds)[-1], 3)
  df_plot <- df_result
  names(df_plot)[-1] <- method_levels <- paste0(names(df_plot)[-1], "(", pts, ")")
  
  if(plot_type=="boxplot"){
    p <- 
      df_plot %>%
      pivot_longer(!n_sim, names_to="method", values_to="nmb") %>%
      mutate(method=factor(method, levels=method_levels)) %>%
      ggplot(aes(method, nmb)) +
      geom_boxplot() +
      geom_jitter(alpha=0.1, width=0.1) +
      theme_bw() +
      labs(
        y="", x="",
        subtitle=glue::glue("auc: {sim_auc}; event_rate: {event_rate}")
      ) +
      scale_y_continuous(labels=scales::dollar_format()) +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  }else{
    get_medians <- function(x, nboot=500){
      m <- median(x)
      
      boots <- map_dbl(
        1:nboot, 
        function(v){
          s <- sample(x, size=length(v), replace=T)
          median(s)
        }
      )
      list(median=m, median_se=sd(boots))
    }
    
    df_plot2 <- 
      df_plot %>%
      pivot_longer(!n_sim, values_to="nmb", names_to="method")
    
    df_plot2 <- as.data.table(df_plot2)[
      ,
      get_medians(x=nmb),
      by = list(method)
    ]
    
    p <-
      df_plot2 %>%
      mutate(method=factor(method, levels=method_levels)) %>%
      ggplot(aes(method, median)) +
      geom_point() +
      geom_errorbar(aes(ymin=median-median_se, ymax=median+median_se, width=0)) +
      theme_bw() +
      labs(
        y="", x="",
        subtitle=glue::glue("auc: {sim_auc}; event_rate: {event_rate}")
      ) +
      scale_y_continuous(labels=scales::dollar_format()) +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  }
  
  if(length(get_what)==1){
    if(get_what=="data"){return(df_result)}
    if(get_what=="plot"){return(p)}
  }else{
    return(list(data=df_result, plot=p))
  }
}

# test_run <- do_simulation(
#   sample_size=500, n_sims=20, n_valid=500, sim_auc=0.7, event_rate=0.03,
#   fx_costs=get_nmb, resample_values=TRUE, get_what=c("data", "plot"), plot_type = "point"
# )
# test_run

```

## search through a grid of combinations of AUC and event rates to see how this influences the differences between probability threshold methods. The same costs were used in all simulations (distributions at top of document) and are resampled separately for training and validation.
#### In the plot below, the columns, from left to right, have increasing AUC. The rows, from top to bottom, have increasing event rates.

### My hot takes:
#### Probability threshold selection method becomes increasingly important as the AUC of the model and the event rate reduces.
#### I think that this is because, for models with very high discrimination, they're able to correctly classify a larger proportion of samples, and there are fewer which are classified differently based on selection method. The difference is greater for smaller event rates because a false negative is the most costly classification, and only the cost-based method is "aware" of this. This is also why, when the event rate is very high, there is not much of a difference between methods (cost-based method is focused on correctly classifying the majority class but so are the other methods).
```{r, fig.height=24, fig.width=12}

library(parallel)
n_cluster <- detectCores()
cl <- makeCluster(n_cluster)
cl <- parallelly::autoStopCluster(cl)

g <- expand.grid(
  sim_auc=c(0.65, 0.75, 0.85, 0.95),
  # event_rate=c(0.01, 0.03, 0.1, 0.3, 0.7, 0.9)
  event_rate=c(0.01, 0.025, 0.05, 0.075, 0.1)
)

clusterExport(cl, {
  c("do_simulation", "g", "get_nmb")
})

invisible(clusterEvalQ(cl, {
  library(tidyverse)
  library(data.table)
  library(cutpointr)
  source("src/inputs.R")
  source("src/utils.R")
  source("src/cutpoint_methods.R")
}))


ll1 <- parallel::parLapply(
  cl,
  1:nrow(g),
  function(i) do_simulation(
    sample_size=500, n_sims=100, n_valid=1000,
    sim_auc=g$sim_auc[i], event_rate=g$event_rate[i],
    fx_costs=get_nmb, get_what="plot", resample_values=TRUE,
    plot_type="point"
  )
)

# ll2 <- parallel::parLapply(
#   cl,
#   1:nrow(g),
#   function(i) do_simulation(
#     sample_size=500, n_sims=100, n_valid=1000,
#     sim_auc=g$sim_auc[i], event_rate=g$event_rate[i],
#     fx_costs=get_nmb, get_what="plot", resample_values=FALSE,
#     plot_type="point"
#   )
# )

cowplot::plot_grid(plotlist=ll1, ncol=length(unique(g$sim_auc)))

# cowplot::plot_grid(plotlist=ll2, ncol=length(unique(g$sim_auc)))

```
