---
title: "Experiment 1"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
source("src/utils.R")
```


Question: What are the differences in NMB between models where the Probability threshold was based on the Youden index versus costs-based selection. (Hospital falls as a use case.)

1. Define costs of a TP, TN, FP, FN of falls classification (option to move this into the loop where costs are sampled from a distributions to account for uncertainty in their estimates in the literature)
    * FP have cost of applying intervention
    * FN have cost of patient fall
    * TP have cost of intervention + cost of fall*(1-effectiveness of intervention on rate of falls)
    * TN are cost $0
2. Determine beta distribution parameters to represent predicted probabilities with an expected value equal to the prevalence (~1-3%?) and approximately similar AUC to currently available models (~0.75?) when evaluating probabilities to outcomes using binomial distribution.
3. For sample sizes (N) in [100, 500, 1000, 5000, 1000]: (repeat 10k times at each sample size)
    * Sample N samples from beta distribution under selected parameters (with or without some error on the parameters)
    * Transform probabilities to events using binomial distribution
    * Select probability thresholds based on Youden index vs costs
    * Evaluate the two thresholds on sample taken from same beta distribution but with n=10000. Estimate mean cost per patient on this validation set.
4. Measure differences in NMB on validation sample dependent on use of Youden index versus cost-based approach to determine threshold.
5. Observe whether this relationship is dependent on the sample size taken


### Define costs
```{r}
treatment_cost <-250
treatment_effect <- 0.1
wtp <- 28000
QALYs_event <- 0.1

cost_vector <- c(
  "TN"=0, 
  "FN"=QALYs_event*wtp, 
  "TP"=QALYs_event*(1-treatment_effect)*wtp, 
  "FP"=treatment_cost
)
```

### Determine appropriate beta distribution for predicted probabilities (prevalence of ~3% and AUC of ~0.75)
```{r}
distribution <- get_beta_preds(beta=35, p=0.03, n=100000, get_what=c("auc", "params", "preds"))

glue::glue("AUC: {round(distribution$auc, 4)}")
glue::glue("Prevalence: {round(mean(distribution$preds$actual), 4)}")
glue::glue("Parameters: alpha={round(distribution$alpha, 4)}; beta={distribution$beta}")
```


### Run simulation
```{r}
sample_sizes <- c(100, 500, 1000)
n_sims <- 500
n_valid <- 1000

df_result <- data.frame(train_sample_size=c(), n_sim=c(), youden_cost=c(), cost_effective_cost=c())


for(n in sample_sizes){
  i <- 0
  while(i < n_sims){
    train_sample <- get_beta_preds(
      alpha=distribution$alpha, 
      beta=distribution$beta, 
      n=n, 
      get_what="preds"
    )$preds
    
    valid_sample <- get_beta_preds(
      alpha=distribution$alpha, 
      beta=distribution$beta, 
      n=n_valid,
      get_what="preds"
    )$preds
    
    if(length(unique(valid_sample$actual))!=2 | length(unique(train_sample$actual))!=2){
      # If there are no cases in either the training or validation sample, then redo sampling.
      next
    }
    
    i <- i+1
    
    thresholds <- get_thresholds(
      predicted=train_sample$predicted, 
      actual=train_sample$actual,
      costs=cost_vector
    )
    
    youden_mean_cost <- classify_samples(
      predicted=valid_sample$predicted,
      actual=valid_sample$actual,
      pt=thresholds$youden,
      costs=cost_vector
    )
    
    cost_effective_mean_cost <- classify_samples(
      predicted=valid_sample$predicted,
      actual=valid_sample$actual,
      pt=thresholds$cost_effective,
      costs=cost_vector
    )
    df_result <- rbind(
      df_result, 
      data.frame(
        train_sample_size=c(n), 
        n_sim=c(i), 
        youden_cost=c(youden_mean_cost), 
        cost_effective_cost=c(cost_effective_mean_cost)
      )
    )
  }
}


df_result %>%
  select(-n_sim) %>%
  pivot_longer(!train_sample_size, names_to="method", values_to="cost") %>%
  ggplot(aes(method, cost)) +
  geom_boxplot() +
  geom_jitter(alpha=0.1, width=0.1) +
  facet_wrap(~train_sample_size) +
  theme_bw() +
  labs(y="Mean cost per patient") +
  scale_y_continuous(labels=scales::dollar_format())
```




